Analyzing the Impact of Input and Label Modifications on CIFAR-10 Classification

### 2025-05-16 PaperForReview.tex
Minor paper tweaks

\paragraph{1. Baseline.}
Original CIFAR-10 inputs and labels. For the baseline, training inputs are only transformed by ToTensor() and normalization using CIFAR-10 mean/std. No other data augmentations such as random cropping or flipping are applied. Test and validation inputs receive the same minimal transformations.

\paragraph{2. Random Label Shuffle.}
Original inputs. Each sample's label (train, val, test) replaced by a random uniform choice from 10 classes.

\paragraph{3. Label Noise (20\%).}
Original inputs. 20\% of sample labels (train, val, test) flipped to a random incorrect class.

\paragraph{4. Input Perturbation.}
Original labels.
\textbf{Training/Validation Inputs:} RandomResizedCrop (32x32, scale (0.6,1.0)), RandomHorizontalFlip (p=0.5), GaussianBlur (kernel 3, sigma (0.1,2.0)), ColorJitter (factors 0.4, hue 0.1), ToTensor, Normalize, RandomErasing~\cite{DBLP:conf/aaai/Zhong0KL020} (p=0.25, scale (0.02,0.2)). Examples in Figure~\ref{fig:perturbed_examples_main}.
\textbf{Test Inputs:} GaussianBlur (kernel 3, sigma 1.0), ToTensor, Normalize.

@@

\paragraph{Baseline.} Achieves 78.26\% Acc@1 and $\kappa=0.7584$.
\paragraph{Random Label Shuffle.} Fails to learn; Acc@1 on random labels is 10.11\%. Against original labels, $\kappa=-0.0134$. Loss high (2.3219).
\paragraph{Label Noise (20\%).} Degrades to 64.52\% Acc@1, $\kappa=0.6058$. Model shows resilience.
\paragraph{Input Perturbation.} Best performance: Acc@1 85.33\% (+7.07\% vs. baseline), $\kappa=0.8370$. Test loss lowest (0.5327). Strong regularization.

>>>>

\paragraph{1. Baseline.}
Original CIFAR-10 inputs and labels. For the baseline, training inputs are only normalized using CIFAR-10 mean/std. No other data augmentations such as random cropping or flipping are applied. Test and validation inputs receive the same minimal transformations.

\paragraph{2. Random Label Shuffle.}
Original inputs. Each sample's label replaced by a random uniform choice from 10 classes.

\paragraph{3. Label Noise (20\%).}
Original inputs. 20\% of sample labels flipped to a random incorrect class.

\paragraph{4. Input Perturbation.}
Original labels.
\textbf{Training/Validation Inputs:} RandomResizedCrop (32x32, scale (0.6,1.0)), RandomHorizontalFlip (p=0.5), GaussianBlur (kernel 3, sigma (0.1,2.0)), ColorJitter (factors 0.4, hue 0.1), RandomErasing~\cite{DBLP:conf/aaai/Zhong0KL020} (p=0.25, scale (0.02,0.2)). Examples in Figure~\ref{fig:perturbed_examples_main}.
\textbf{Test Inputs:} GaussianBlur (kernel 3, sigma 1.0).

@@

\paragraph{Baseline.} Achieves 78.26\% Acc@1 and $\kappa=0.7584$.
\paragraph{Random Label Shuffle.} Fails to learn; Acc@1 on random labels is 10.11\%. Against original labels, $\kappa=-0.0134$. Loss high (2.3219). Confusion matrix (Table~\ref{fig:cm_shuffle_main}) shows output collapsed to class \texttt{AUTOMOBILE}.
\paragraph{Label Noise (20\%).} Degrades to 64.52\% Acc@1, $\kappa=0.6058$. Model shows resilience.
\paragraph{Input Perturbation.} Best performance: Acc@1 85.33\% (+7.07\% vs. baseline), $\kappa=0.8370$. Test loss lowest (0.5327). Strong regularization.
